CP_MSSA

### 2025-03-17 Code/R/Research/CP_MSSA.Rmd
minor fix

  rec <- lapply(Ls_cp, function(L)
    tens_mssa_reconstruct(
      x,
      L,
      groups = groups_cp,
      decomp = "cp",
      status = FALSE,
      tol = tol,
      max_iter = max_iter,
      start = "svd"
    ))
  sapply(rec, function(r)
    colMeans(abs(Reduce("+", r) - s)^2))
}
```

@@

  rec <- list(
    mssa = reconstruct(ssa(x, L = L_mssa, kind = "mssa"), groups = groups_mssa),
    cp_mssa = tens_mssa_reconstruct(
      x,
      L_cp,
      groups = groups_cp,
      decomp = "cp",
      status = FALSE,
      tol = tol,
      max_iter = max_iter,
      start = "svd"
    ),
    ho_mssa = tens_mssa_reconstruct(
      x,
      L = L_ho,
      groups = groups_mssa,
      groups3 = groups3,
      decomp = "hooi",
      status = FALSE,
      tol = tol,
      max_iter = max_iter
    )
  )
  sapply(rec, function(r)
    colMeans(abs(Reduce("+", r) - s)^2))
}
```

>>>>

  rec <- lapply(Ls_cp, function(L)
    tens_mssa_reconstruct(
      x,
      L,
      groups = groups_cp,
      decomp = "cp",
      status = FALSE,
      tol = tol,
      max_iter = max_iter,
      cp_start = "svd"
    ))
  sapply(rec, function(r)
    colMeans(abs(Reduce("+", r) - s)^2))
}
```

@@

  rec <- list(
    mssa = reconstruct(ssa(x, L = L_mssa, kind = "mssa"), groups = groups_mssa),
    cp_mssa = tens_mssa_reconstruct(
      x,
      L_cp,
      groups = groups_cp,
      decomp = "cp",
      status = FALSE,
      tol = tol,
      max_iter = max_iter,
      cp_start = "svd"
    ),
    ho_mssa = tens_mssa_reconstruct(
      x,
      L = L_ho,
      groups = groups_mssa,
      groups3 = groups3,
      decomp = "hooi",
      status = FALSE,
      tol = tol,
      max_iter = max_iter
    )
  )
  sapply(rec, function(r)
    colMeans(abs(Reduce("+", r) - s)^2))
}
```
